%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------
  
\end{document}

\firstname{Martin} % Your first name
\familyname{Konicek} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
%\address{123 Broadway}{City, State 12345}
%\mobile{+44 hidden}
%\email{hidden}
\homepage{coding-time.co}{coding-time.co} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2005--2011}{MSc in Computer Science}{Faculty of Mathematics and Physics, Charles University in Prague}{Graduated with honours, awarded merit scholarship}{}{}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

%See an online version of this CV with links and videos: \href{http://bit.ly/2Dyr2Y5}{http://bit.ly/2Dyr2Y5} \newline

% \subsection{Software engineering}

\cventry[0.4em]{\small 10/2018--present}{Synthace}{Tech Lead - Full Stack}{}{}{Synthace makes software for biologists. About half the employees are biologists and we have a lab with high-tech lab robots. Most of the customers are pharma companies researching new drugs. The product can be described as a visual IDE for programming lab robots. I was the second engineer to join the full-stack team and introduced TypeScript at the company. I was a tech lead of two projects which both shipped successfully and I am now leading a third project. This involves code review, mentoring engineers, running team meetings, project management, coordinating with the rest of the company: engineering teams, lab scientists, our sales and customer success teams. Technologies: TypeScript, React, Node, .NET.}

%\cventry[0.4em]{\small 05/2018--06/2018}{Deliveroo}{Software Engineer - contract}{}{}{Helped the Logistics team port a service from Ruby to Rust. The service decides which Deliveroo rider picks up each order. Technologies: Ruby, Rust.}

%\cventry[0.4em]{\small 10/2017--03/2018}{Monzo}{Software Engineer - Android}{}{}{Built features in the Monzo Android app. Technologies: Kotlin, RxJava.}

\cventry[0.4em]{\small 09/2013--05/2017}{Facebook}{Software Engineer - Developer Infrastructure}{}{}{The Developer Infrastructure org at Facebook builds frameworks and tools for developers. I was the tech lead for the open source project React Native for Android. I made the initial technical decisions, worked on features together with the team, did project management and ran weekly meetings. I was the point of contact for the team at Microsoft building React Native for Windows, and later for the team building the Skype mobile app. I worked with external contributors from AirBnb and other companies. React Native became Facebook's most active open source project in terms of external contributions. For my next project I joined the ads team to build a screen in the Facebook app using React Native. My goal was to evaluate and improve the developer experience of React Native. I took the initiative to revamp the internal documentation used by hundreds of engineers at Facebook. Before working on React Native I was one of the first engineers on a team that delivered a system for automated performance testing of mobile apps. I helped take the system from a prototype to being widely used by teams across Facebook. I did a few dozen technical interviews, was a bootcamp mentor and mentored one intern. Technologies: Android, JavaScript, Hack (PHP), Python.}

\cventry[0.4em]{\small 02/2012--06/2013}{Commercetools}{Software Engineer - Scala Backend, Java SDK}{}{}{Designed a Java SDK for an e-commerce PaaS. Implemented in-memory joins on top of MongoDB and other parts of the Scala backend, worked on parts of the JavaScript frontend. Technologies: Java, Scala, JavaScript.}

\cventry[0.4em]{\small 03/2011--08/2011}{nangu.tv}{Software Engineer - Hadoop}{}{}{Researched technologies and best practices for large-volume log collection and analysis. Technologies: Hive, Flume, Pig, HBase.}

\cventry[0.4em]{\small 01/2011--02/2011}{mobreator}{Software Engineer - Android}{}{}{Built an Android app that encodes images into sound and decodes them back on nearby devices using the microphone. Coming up with the way to encode the image data as sound and decode it was exciting.}

\cventry[0.4em]{\small 04/2010--09/2010}{SharpDevelop IDE}{Successful participant at Google Summer of Code 2010}{}{}{Implemented a new refactoring framework, improved code completion based on own ideas. SharpDevelop is an open source IDE downloaded about 2000 times a day. Technologies: C{\#}.}

% \subsection{Soft skills}

\cventry[0.4em]{\small 04/2010--04/2010}{Participant at McKinsey Horizon event}{}{}{}{2/100 applicants selected from the Czech Republic. Problem solving, soft-skills training, introduction to business consulting.}

\cventry[0.4em]{\small 04/2009--09/2009}{SharpDevelop IDE}{Successful participant at Google Summer of Code 2009}{}{}{Proposed and implemented innovative debugging features, e.g. visualization of object graphs.}

\cventry[0.4em]{\small 12/2008--10/2010}{TaskConnect}{Tech Lead - .NET}{}{}{Technical lead of a team of five, working on core parts of the application, such as the plugin architecture and background sync. Introduced continuous integration. Technologies: C{\#}, COM.}

\cventry[0.4em]{\small 10/2008--02/2010}{Charles University in Prague}{Assistant Teacher}{}{}{Taught a practical introductory class to computer science (pointers, trees, recursion) for a group of 20 students. Evaluated student projects.}

\cventry[0.4em]{\small 06/2007--04/2009}{e-fractal.cz}{Sotware Engineer - .NET}{}{}{Designed a program to synchronize Microsoft Exchange contacts with the phonecopy.com service. Worked on websites for customers. Technologies: C{\#}.}

\section{Languages}
\cvlanguage{English}{Fluent}{}
\cvlanguage{Spanish}{Intermediate}{}
\cvlanguage{German}{Basic}{}

%\section{Interests}
%\cvline{Natural languages}{I would like to learn Chinese.}

\section{References}

\cvline{Yael Ben Dov}{My manager at Synthace}
\cvline{Alberto Morabito}{An engineer I mentored at Synthace}
\cvline{Olivia Bishop}{My manager on the React Native team at Facebook}
\cvline{Jim Purbrick}{My manager on the continuous mobile testing team at Facebook}
\cvline{Kevin Lacker}{My manager on the open source team at Facebook}
\cvline{Prof. Daniel Kral}{My supervisor while I was teaching at Charles University in Prague}
\cvline{David Srbecky}{My mentor during Google Summer of Code, currently works at Google}

\section{Online}
%\cvline{}{Online version of this CV with links and videos: \href{http://bit.ly/2Dyr2Y5}{http://bit.ly/2Dyr2Y5}}
\cvline{}{Blog: \href{https://coding-time.co}{https://coding-time.co}}
\cvline{}{StackOverflow: \href{https://stackoverflow.com/users/90998/martin-konicek}{https://stackoverflow.com/users/90998/martin-konicek}}
\cvline{}{GitHub: \href{https://github.com/mkonicek}{https://github.com/mkonicek}}
%\cvline{}{Twitter: \href{https://twitter.com/martinkonicek}{https://twitter.com/martinkonicek}}

\end{document}